BDS MPhil

### 2024-05-21 meetings/summary.qmd
ignore pngs in artifacts, monitor training, constant lr optimizer

**Setting**

- Advertising claims with meta information & ratings

@@

- Novel "summary embeddings", that make an LLM generate a specific ad-claim.

@@

@@

:::
::: {.column}
![2D-generation space.](./figures/slides_pitch.png)
:::
:::

>>>>

@@

- Novel Method: A Summary Embeddings, that make an LLM generate a specific ad-claim.

**Data**

- Advertising claims with meta information & ratings from choice-experiment

@@

:::
::: {.column}
![2D-generation space](./figures/slides_pitch.png)
:::
:::

@@
